\systemEnding: Bootstrapping Domain-Specific Languages for Neurally-Guided Bayesian Program Learning

### 2019-01-09 archive.tex
added some dreams to the deep logo figure

    \draw[->] (p1.south) -- (square.north);
    \draw[->] (p2.south) -- (circle.north);
    \draw[->] (p3.south) -- (semi.north);
    \draw[->] (p2.south) -- (snow.west);
    \draw[->] (p2.south) -- (pu.east);
    \draw[->] (p3.south) to[out=320,in=45] (line.east);
    \draw[->] (p3.south) to[out=200,in=120] (snow.west);

@@

    \draw [dashed] ([xshift=0.5cm,yshift=-0.25\verticalSpacing]programLabel.east) -- ([xshift=15cm,yshift=-0.25\verticalSpacing]programLabel.east);
    \node[align=left,anchor=center] at ([xshift=14cm,yshift=-0.3\verticalSpacing]programLabel.east) {\large $\uparrow$\;system inputs\\\\\\\large $\downarrow$\;system outputs};
  \end{tikzpicture}
  \caption{Two of the six domains we apply our system to. Agent observes tasks (top rows) which it solves by writing programs (middle rows) while jointly growing a library (DSL; bottom rows). Learned DSLs rediscover multiple higher-order functions (\code{filter} for list functions and rotational symmetry for generative graphics). Learned DSL components call each other (arrows).}  \label{exampleDSL}
\end{figure}

>>>>

    \draw[->] (p1.south) -- (square.north);
    \draw[->] (p2.south) -- (circle.north);
    \draw[->] (p3.south) -- (semi.north);
    \draw[->] (p2.south) -- (snow.west);
    \draw[->] (p2.south) -- (pu.east);
    \draw[->] (p3.south) to[out=190,in=120] (line.west);
    \draw[->] (p3.south) to[out=200,in=120] (snow.west);

@@

    \node[align=center,rotate=90] at ([xshift=1cm]snow.east) {$\underbrace{\hspace{6cm}}_{\text{\normalsize \textbf{\textsc{Dreams}: Samples from DSL}}}$};

    \node at ([xshift=3cm]semi.east) {\includegraphics[width = 1.5cm]{figures/finalDreams/63smooth_pretty}};
    \node at ([xshift=3cm]snow.east) {\includegraphics[width = 1.5cm]{figures/finalDreams/400smooth_pretty}};
    \node at ([xshift=3cm]line.east) {\includegraphics[width = 1.5cm]{figures/finalDreams/399smooth_pretty}};
  \end{tikzpicture}
  \caption{Two of the six domains we apply our system to. Agent observes tasks (top rows) which it solves by writing programs (middle rows) while jointly growing a library (DSL; bottom rows). Learned DSLs rediscover multiple higher-order functions (\code{filter} for list functions and rotational symmetry for generative graphics). Learned DSL components call each other (arrows).}  \label{exampleDSL}
\end{figure}
